### 2020-08-20 8_case_study.tex
Fiddle with TensorFlow paragraph.

The Task Bench implementation for TensorFlow uses aggressive loop
unrolling to minimize overhead, and this initially resulted in the
entire graph being marked constant. TensorFlow performs optimizations
on task graphs prior to execution, including a constant folding
pass. These optimizations are performed on a single core. In the case
of Task Bench, this resulted in sequential execution of the entire
graph, resulting in experiments timing out. As a workaround,
additional inputs can be fed to nodes in the graph to make them
non-constant, forcing them to be executed by TensorFlow's normal
scheduler. Though this was exacerbated by Task Bench's approach to
unrolling loops, it affects any task graph with constants that are
expensive to compute where the users may wish to perform
constant-folding in parallel.

>>>>

TensorFlow performs optimizations on task graphs prior to execution,
including a constant folding pass. The Task Bench implementation uses
aggressive loop unrolling to minimize overheads, resulting in the task
graph being marked as constant. Because TensorFlow optimizations are
performed on a single core, this resulted in sequential execution of
the entire graph, and Task Bench experiments timed out. As a
workaround, additional inputs can be fed to nodes in the graph to make
them non-constant, forcing them to be executed by TensorFlow's normal
scheduler. Though this was exacerbated by Task Bench's approach to
unrolling loops, it affects any task graph with constants that are
expensive to compute where the users may wish to perform
constant-folding in parallel.
